Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-28 journal/article.tex
T: Change leaders

A significant change effort requires entities in the organization who take
leadership in the change.

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        Type of leading change         &  Described in  \\
        \midrule
        Agile task group foor coordinating change   &
                P4, P18, P21, P23, P25, P30, P40, P41,
                P43, P45, P48, P49, P50  \\
        \bottomrule
    \end{tabular}
    \caption{Which entities were leading change in the agile transformation}
    \label{table:transformation_leadership}
\end{table}

@@

Many organizations formed an agile task force or similar entity for coordinating
and leading the change. It was typical that in the beginning of the
transformation, or when it had been acknowledged that the old model had
problems, a work group was founded for coordinating the changes to be done. The
change team usually consisted of management personnel [P43, P50], and was
reinforced with external agile consultants [P18, P21, P25, P30]. Some cases
highlighted that the team had a cross organizational staff who were familiar
with the varying functions that would be affected by changes [P4, P21, P41,
P48]. It was important that theere was a group of people who were strongly
committed to making a change happen [P43].

The tasks of the change team included first finding an alternative delivery
method to solve problems in the old model [P21, P30]. During the transformation
the team stimulated agile adoption in the organization [P18, P45, P49]. Examples
on their tasks were informing people on the agile model [P4], educating and
coaching [P45, P48, P49], creating an agile cookbook [P23], and organizing
presentations and workshops [P25, P41]. The change team also assessed the
success of transformed teams, and worked for repeating their success across the
organization [P40, P41].
% The team was also empowered to remove the impediments they discovered [P50].

@@

>>>>

A significant change effort requires entities in the organization who take
leadership in the change. Getting a large group of people aligned towards a
common goal, in many cases a completely new way of working, requires that
someone takes charge for the undertaking.

@@

Leadership for change showed on all organizational levels.
% The ways how change was lead was similar on each level.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        Change leaders         &  Described in  \\
        \midrule
        High-up change leaders or sponsors  &
                P3, P5, P24, P31, P36, P38, P46, P49  \\
        Change leaders on other organizational levels  &
                P2, P6, P9, P14, P17, P18, P27  \\
        Agile task group for coordinating change   &
                P4, P16, P18, P21, P23, P25, P30, P40, P41,
                P43, P45, P48, P49, P50  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of entities leading change in the agile transformation}
    \label{table:transformation_leadership}
\end{table}

% High-up change leaders

In many cases it was described that the change was initiated by a limited number
of people in high-up positions. In these cases typical positions attributed for
giving the initial push for change were CxO's, vice presidents, and directors.
In these cases it was highlighted that one or very few high-up persons affected
significantly the start or expansion of the agile transformation. In some cases
the change leader was a new hire [P5, P38, P46].

The pressence of a high-up manager was described to underline the organization's
commitment for change when dealing with employees or other stakeholders [P24].
The firm commitment of the high-up leader was key in keeping the agile
transformation on course in cases where objections or other problems arose [P5,
P14, P36, P46]. Another important role of the change leader was to persuade and
work for getting other people raise an interest in agile methods [P3, P31, P38,
P46, P49].

@@

Many organizations formed an agile task force or similar entity for coordinating
and leading the change. It was typical that in the beginning of the
transformation, or when it had been acknowledged that the old model had
problems, a work group was founded for coordinating the changes to be done. The
change team usually consisted of management personnel [P43, P50], and was
reinforced with external agile consultants [P18, P21, P25, P30]. Some cases
highlighted that the team had a cross organizational staff who were familiar
with the varying functions that would be affected by changes [P4, P16, P21, P41,
P48]. It was important that theere was a group of people who were strongly
committed to making a change happen [P43].

The tasks of the change team included first finding an alternative delivery
method to solve problems in the old model [P21, P30]. During the transformation
the team stimulated agile adoption in the organization [P18, P45, P49]. Examples
on their tasks were informing people on the agile model [P4], educating and
coaching [P16, P45, P48, P49], creating an agile cookbook [P23], and organizing
presentations and workshops [P25, P41]. The change team also assessed the
success of transformed teams, and worked for repeating their success across the
organization [P16, P40, P41]. Still one characteristic was that the team was
empowered to act on impediments they discovered [P16, P50].

% Other change leaders

Leadership for change emerged also on other organizational levels. In many cases
these change leaders were still in management positions [P14, P18, P17]. There
were also agile champions in teams who drove the change on a grassroots level
[P6, P9, P27].
As with higher-ups, these people worked for making agile methods familiar [P2,
P6, P9, P17], making change stick [P2, P18], and persuaded others to use agile
methods [P2, P9, P14].
Benefield [P6] describes that people in teams were well able to adjust the
application of the agile process as they were familiar with the problems at
hands. It was howerver hard to find people who both understood the agile
principles well, and knew how to coach within the team [P6].
% Also coaches in [P2], and a team in [P16]

Chung and Drummond [P9] give a further description of grassroots level
leadership. Yahoo! initially used a team of coaches to help applying agile, but
the coach team failed to make agile take root. The coaches were later disbanded
due to reductions in budget. The agile practitioners in teams took over the
leadership for the continued application of agile [P9].

@@

* A qualitative interpretation requires much text. Therefore the results got
  long. See ``Meta-ethnography''.
